Algorithmic detection of conserved quantities for finite-difference schemes\thanks{Supported by King Abdullah University of Science and Technology (KAUST) baseline funds and KAUST OSR-CRG2021-4674.}

### 2023-05-07 Papers/Paper CASC format/paper.tex
various

{\color{red}ADD HERE TIME EXPLICIT EXAMPLE WITH PARAMETERS - DISCUSS WITH RICARDO THE ISSUE}

{\color{red} DG HERE}

@@

	\label{step3} Reduce $\mathcal{T}$ by using the Gr{\"o}bner basis generated by the translated scheme in two different ways
	\label{step3a} (a) Using the lexicographic order
	\label{step3b} (b) Using the explicit elimination order\;

>>>>

{\color{red}ADD HERE TIME EXPLICIT EXAMPLE WITH PARAMETERS}

@@

	\label{step3} Reduce $\mathcal{T}$ by using {\color{red} the Gr{\"o}bner basis} generated by the translated scheme in two different ways
	\label{step3a} (a) Using the lexicographic order
	\label{step3b} (b) Using the explicit elimination order\;
